Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-04-18 2016-Weak-FH-Bisim/WeakBisim.tex
Definition 11 improved

Intuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
We define $\Id(s)$ as the identity function on variables of state s.
\begin{definition}[Non-observability of silent actions]\label{def:Non-ObsTau}
An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
\begin{enumerate}
\item
\[ \openrule
         {
           (j\mapsto\tau),\True,\Id(s)}
         {s \OTarrow {\tau} s}
         \in \mathcal{T}
\]
and 
\item for all $A$, $\alpha$,  $s$, $\Post$ and $s'$ such that
\[ \openrule
         {
           A,\Pred,\Post}
         {s \OTarrow {\alpha} s'}
         \in \mathcal{T} \] If there is a $j$ such that $A(j)=\tau$ then we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s)
\]
\end{enumerate}
\end{definition}
The first statement of the definition state that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e. cannot change its internal state because a hole did a $\tau$ transition. The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a silent action from a hole.

>>>>

Intuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
We define $\Id(s)$ as the identity function on variables of state s.
\begin{definition}[Non-observability of silent actions]\label{def:Non-ObsTau}
An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
\begin{enumerate}
\item
\[ \openrule
         {
           (j\mapsto\tau),\True,\Id(s)}
         {s \OTarrow {\tau} s}
         \in \mathcal{T}
\]
and 
\item for all $A$, $\alpha$,  $s$, $\Post$ and $s'$ such that
\[ \openrule
         {
           \beta_j^{j\in J},\Pred,\Post}
         {s \OTarrow {\alpha} s'}
         \in \mathcal{T} \] If there is a $j$ such that $\beta_j=\tau$ then we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s) \land J=\{j\})
\]
\end{enumerate}
\end{definition}
The first statement of the definition state that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e. cannot change its internal state because a hole did a $\tau$ transition. The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a silent action from a hole. The condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform silent transitions too (because these silent actions cannot be observed).
